---
title: "diagnoses"
author: "Tarun"
date: "2/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dbplyr)
library(RMySQL)
library(dplyr)
library(tidyr)
library(lubridate)
library(readr)
library(stringr)

# con <- dbConnect(MySQL(),  
#                  user="tnarasim",
#                  password=rstudioapi::askForPassword("Database password"), 
#                  host="shahlab-db1.stanford.edu", 
#                  port=3306,
#                  db = "stride7"
# )

con2 <- dbConnect(MySQL(),  
                 user="tnarasim",
                 password=rstudioapi::askForPassword("Database password"), 
                 host="shahlab-db1.stanford.edu", 
                 port=3306,
                 db = "stride7_dictionaries"
)

dx_dict_df <- con2 %>%
  tbl("shc_clarity_edg") %>% 
  select( dx_id, dx_name, contains("icd") ) %>% 
  collect()

dbDisconnect(con2)
```


# Find dx codes for autoimmune hypothroidism
```{r}
# filter( dx_dict_df, current_icd10_list=="E06.3"  )

# test <- dx_dict_df %>% 
#   filter( (grepl("[aA]utoimmune" , dx_name ) & 
#           grepl("[hH]ypo.?[tT]hyroid" , dx_name )) | 
#           grepl( "[hH]ashimoto" , dx_name )
#        ) %>% 
#   arrange(current_icd9_list)
# View(test)

auto_hypo_icd9 <- "245.2"

auto_hypo_df <- dx_dict_df %>% 
  filter(current_icd9_list=="245.2" | dx_id== "193146" | dx_id=="1080318" | dx_id=="1794594")

auto_hypo_dx_id <- unique(auto_hypo_df$dx_id)

```

- ICD9: 245.2 (?)
  - Might include other diseases
- ICD10: E06.3
- find all dx_id with "autoimmune" and correct ICD9

- Hashimoto's disease (aka chronic lymphocytic thyroiditis)

# Find dx codes for celiac 

```{r}

# test <- dx_dict_df %>%
#   filter( str_detect(dx_name, "[Cc]eliac") & 
#           str_detect(dx_name, "[dD]isease") ) %>% 
#   arrange(current_icd9_list)
# View(test)


celiac_icd9 <- "579.0"

celiac_df <- dx_dict_df %>% 
  filter(current_icd9_list=="579.0" | dx_id== "1294744")

celiac_dx_id <- unique(celiac_df$dx_id)

```


# Find dx codes for T1DM 

```{r t1dm}
# test <- dx_dict_df %>%
#   filter( str_detect(dx_name, "type 1 diabetes mellitus") ) %>%
#   arrange(current_icd9_list)
# View(test)


t1dm_icd9 <- c("250.01", "250.03")

t1dm_df <- dx_dict_df %>% 
  filter(current_icd9_list %in% t1dm_icd9)

t1dm_dx_id <- unique(t1dm_df$dx_id)

```


# Find dx codes for multiple sclerosis 

```{r ms}

# test <- dx_dict_df %>%
#   filter( str_detect(dx_name, "multiple sclerosis") ) %>%
#   arrange(current_icd9_list)
# View(test)
# 
# test <- dx_dict_df %>%
#   filter( current_icd9_list=="340") %>%
#   arrange(dx_id)
# View(test)

ms_icd9 <- c("340")

ms_df <- dx_dict_df %>% 
  filter(current_icd9_list %in% ms_icd9)

ms_dx_id <- unique(ms_df$dx_id)


```


# Find dx codes for rheumatoid arthritis

```{r rheumatoid arthritis}

rheu_ar_icd9 <- c("714.0")

rheu_ar_df <- dx_dict_df %>% 
  filter(current_icd9_list %in% rheu_ar_icd9)

rheu_ar_dx_id <- unique(rheu_ar_df$dx_id)


```


# Find dx codes for Graves disease

```{r graves}

grav_icd9 <- c("242.0")

grav_df <- dx_dict_df %>% 
  filter(current_icd9_list %in% grav_icd9)

grav_dx_id <- unique(grav_df$dx_id)


```


# Find dx codes for SLE

```{r sle}

sle_icd9 <- c("710.0")

sle_df <- dx_dict_df %>% 
  filter(current_icd9_list %in% sle_icd9)

sle_dx_id <- unique(sle_df$dx_id)

```



# Save all variables

```{r}

save( auto_hypo_dx_id, auto_hypo_icd9, 
      celiac_dx_id, celiac_icd9, 
      t1dm_dx_id, t1dm_icd9,
      ms_icd9, ms_dx_id, 
      rheu_ar_icd9, rheu_ar_dx_id, 
      grav_icd9, grav_dx_id, 
      sle_icd9, sle_dx_id, 
      file="/Users/Tarun/Documents/BIO_RESEARCH/diagnoses/diagnosis_codes"
      )

load( "/Users/Tarun/Documents/BIO_RESEARCH/diagnoses/diagnosis_codes" )
```

